market-justice-preferences

### 2024-05-15 paper.qmd
render paper

---
title: "market-justice-preferences"
author: "Equipo EDUMER"
format: pdf
editor: visual
bibliography: "input/bib/just-ineq-merit.bib"
link-citations: true
---

@@

##

>>>>

---
format:
  html:
    keep-tex: true
editor: visual
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
link-citations: true
mainfont: Times New Roman
---

@@

{{< include 01-introduction.qmd >}}

{{< include 02-antecedentes.qmd >}}

{{< include 03-methods.qmd >}}

{{< include 04-analisis.qmd >}}

{{< include 05-conclusiones.qmd >}}

{{< include 06-anexos.qmd >}}
